### 2020-11-30 doc/manuscript/Dow_manuscript.Rmd
added another reference to incorporate
update climwin fig caption
#26

climwin_caption <- "Figure 3. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- (1ST ROW) and diffuse-porous (2ND ROW) trees at SCBI (FIRST COLUMN) and Harvard Forest (SECOND COLUMN). Shown are matrices of linear coefficients of first-order linear regressions between temperature and DOY_25, where Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: May 4 at SCBI, May 15 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black boxes indicate the optimal window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF)."

@@

>>>>

climwin_caption <- "Figure 3. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest. Shown are matrices of linear coefficients of first-order linear regressions between temperature and DOY_25, where Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: May 4 at SCBI, May 15 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black boxes indicate the optimal window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF)."

@@

@delgado_differences_2020
